Detecting Stylistic Variation in Pop Production using the Spotify API

### 2023-11-09 outputs/paper/paper.qmd
latex wrestling

add model here

>>>>

The training process for the RF model can be summarized as follows:

1.  For each iteration ( b = 1 ) to ( B ):
    a.  Draw a bootstrap sample ( Z\^\* ) of size ( N ) from the training data.
    b.  Grow a random-forest tree ( T_b ) to the bootstrapped data by recursively performing the following steps for each terminal node of the tree until the minimum node size ( n\_{\text{min}} ) is reached:
        i.  Select ( m ) predictors at random from the ( p ) predictors.
        ii. Determine the best predictor and split-point among the ( m ).
        iii. Split the node into two daughter nodes.
2.  The ensemble of trees ( { T_b }\^B\_{b=1} ) constitutes the random forest model.

For a new instance ( x ), the RF model prediction ( \hat{C}\^{\text{RF}}(x) ) is determined by the majority vote from the ensemble of trees:

\[ \hat{C}\^{\text{RF}}(x) = \text{majority vote} \left{ \hat{C}*b(x)* \right}\^B{b=1} \]

Where ( \hat{C}\_b(x) ) is the class prediction of the ( b )-th tree.
